Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
rearrange to separate the plant phenomics details from the technical details
reduce details about PODD

CSIRO ASC shared facilities \cite{ASC} are used to process the raw
PlantScan\textsuperscript{\texttrademark} data to derive data products (meshes).
Raw data and meshes are collected using the BagIt format \cite{Kunze2011} and
stored in the ASC archival system. ASC High Performance Compute (HPC) hosts
(systems with high processor count and large memory) are taken advantage of to
create and verify bags more rapidly than would be possible on conventional
computer systems. The DAP to store collections of
PlantScan\textsuperscript{\texttrademark} 
raw images and processed mesh data as bags . Raw data from
PlantScan\textsuperscript{\texttrademark} 
local storage (HRPPC-Store) and data processed on HPC hosts are transferred to
ASC bulk storage where image and mesh files are organised in folders by batch,
then barcode number, then subfolders for each image file type (e.g. RGB images,
IR images, LiDAR) and meshes. Bag creation is carried out via an allocated ASC
HPC job.

Currently, one bag is equivalent to a single batch scanned on the
PlantScan\textsuperscript{\texttrademark}
local software system, which usually means the same kind of plant with different
genotypes scanned under one  experiment configuration profile.  
% However the
% naming, content and amount of data in a bag are flexible and depend upon the
% intention of the bag. For example, multiple batches can be packed into one bag
% when the batches come from one plant’s scans at different time points. The
% multi-threaded BagIt tool is called on the ASC HPC host to create a bag that is
% then compressed into a single file containing a top-level data folder, a
% manifest file that contains checksums for every data file, and tag files that
% contain the metadata description of the bag just packed. 
The metadata required for a DAP publication is created and the bag transferred
to the DAP staging area via SFTP (SSH File Transfer Protocol). After publication
of the DAP collection, the data from PlantScan\textsuperscript{\texttrademark}
for the given project becomes
discoverable via DAP. In addition, experiment reports, published papers, and
sensor configurations can either be made accessible via a DAP collection's
``related materials'' links, other metadata fields, or within the collection's
data (e.g. bag).

@@

The PODD ontology allows sparse annotation of data and results, so scientists
are not required to annotate all of their data with links to shared ontologies
by default. However, the system is extensible, so in future such a requirement
could be added in a new version of the PODD ontology while maintaining backwards
compatibility with previous experiments that may be published or immutable.

@@

PODD implements support for Content Negotiation, with common RDF serialisations
supported in addition to HTML pages that are encoded with RDFa (RDF in
Attributes). Although most non-human agents will receive an RDF formatted
document when they resolve a PODD URI, if a PODD HTML page is saved the
annotations can still be retrieved using RDFa.

>>>>

CSIRO ASC shared facilities \cite{ASC} are used to process the raw
PlantScan\textsuperscript{\texttrademark} data to derive data products (meshes).
Raw data and meshes are collected using the BagIt format \cite{Kunze2011} and
stored in the ASC archival system. ASC High Performance Compute (HPC) hosts
(systems with high processor count and large memory) are taken advantage of to
create and verify bags more rapidly than would be possible on conventional
computer systems. The DAP to store collections of
PlantScan\textsuperscript{\texttrademark} 
raw images and processed mesh data as bags. Currently, one bag is equivalent to
a single batch scanned on the
PlantScan\textsuperscript{\texttrademark}
local software system, which usually means the same kind of plant with different
genotypes scanned under one  experiment configuration profile.

Raw data from
PlantScan\textsuperscript{\texttrademark} 
local storage (HRPPC-Store) and data processed on HPC hosts are transferred to
ASC bulk storage where image and mesh files are organised in folders by batch,
then barcode number, then subfolders for each image file type (e.g. RGB images,
IR images, LiDAR) and meshes. Bag creation is carried out via an allocated ASC
HPC job.
% However the
% naming, content and amount of data in a bag are flexible and depend upon the
% intention of the bag. For example, multiple batches can be packed into one bag
% when the batches come from one plant’s scans at different time points. The
% multi-threaded BagIt tool is called on the ASC HPC host to create a bag that is
% then compressed into a single file containing a top-level data folder, a
% manifest file that contains checksums for every data file, and tag files that
% contain the metadata description of the bag just packed. 
The metadata required for a DAP publication is created and the bag transferred
to the DAP staging area via SFTP (SSH File Transfer Protocol). After publication
of the DAP collection, the data from PlantScan\textsuperscript{\texttrademark}
for the given project becomes
discoverable via DAP. In addition, experiment reports, published papers, and
sensor configurations can either be made accessible via a DAP collection's
``related materials'' links, other metadata fields, or within the collection's
data (e.g. bag).

@@

% The PODD ontology allows sparse annotation of data and results, so scientists
% are not required to annotate all of their data with links to shared ontologies
% by default. However, the system is extensible, so in future such a requirement
% could be added in a new version of the PODD ontology while maintaining backwards
% compatibility with previous experiments that may be published or immutable.

@@

% PODD implements support for Content Negotiation, with common RDF serialisations
% supported in addition to HTML pages that are encoded with RDFa (RDF in
% Attributes). Although most non-human agents will receive an RDF formatted
% document when they resolve a PODD URI, if a PODD HTML page is saved the
% annotations can still be retrieved using RDFa.
